---
title: "Linear Regression Practice"
author: "Brady Chiu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    css: ./formatting.css
    code_folding: hide
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 4
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 4
---

# TL;DR

```{r message=FALSE, warning=FALSE, cache=FALSE}
knitr::read_chunk("../code/main.R")
knitr::opts_chunk$set(fig.height=5, fig.width=8)
```
```{r notes, message=FALSE, warning=FALSE, cache=FALSE}
```
```{r setup, message=FALSE, warning=FALSE, cache=TRUE}
```
```{r functions, message=FALSE, warning=FALSE, cache=TRUE}
```
```{r parameters, message=FALSE, warning=FALSE, cache=TRUE}
```

# Data

* We'll use the __swiss__ data from the __datasets__ package in R
* We see no significant outliers and fairly normal distributions, confirming our data is good to go

```{r data, message=FALSE, warning=FALSE, cache=TRUE}
```

# Multicolinearity

* Before we run our model, we'll check our data for multicolinearity

## Correlation Plot

* We see somewhat high correlation between Examination and Education, so we'll need to remove one of them in order to avoid multicolinearity

```{r multicolinearity_corrplot, message=FALSE, warning=FALSE, cache=TRUE}
```

## Principal Component Analysis

* Our PCA shows that 3 components account for >99% of the variance
  * Catholic, Agricultre, and Education are the strongest components

```{r multicolinearity_pca, message=FALSE, warning=FALSE, cache=TRUE}
```

## Variance Inflation Factor

* Our VIF analysis confirms that Examination is the highest inflator of variance and moderately correlated

```{r multicolinearity_vif, message=FALSE, warning=FALSE, cache=TRUE}
```

# Model

## Model Selection

```{r linear_model, message=FALSE, warning=FALSE, cache=TRUE}
```

# Results

```{r results, message=FALSE, warning=FALSE, cache=TRUE}
```